### 2021-03-07 paper_1.tex
update
Points

>>>>

\subsubsection{Bayesian Inference With Contour Guidance}
Bayesian inference gives the possibility to calculate the probability that a 
pixel x may belong to a salient structure s. This probability is computed as:
$$ p(x|s) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
finally $ p(s)=Sw $ represents the CBSP value. The implementation 
details are as follows.
\begin{enumerate}
    \item \emph{Predict the size of Potential Structure}: useful for obtaining $ p(x|s) $ and 
    $ p(x|b) $. This procedure, through a binarization of the map obtained 
    from $ p(s) $, separates the salient structures from the background, all 
    through the use of a threshold. This threshold is calculated using the 
    local parameters (color, luminance, etc.), a percentage not greater than 
    50\% useful to denote the size of the salient structure, an initial weight 
    and finally two sets of pixels corresponding to the background and the 
    foreground (salient structure).
    \item \emph{Evaluate the Importance of Each Feature}:  
\end{enumerate}
